\section{FAQ}

\subsection*{Is there any log file?}
\begin{itemize}
\item \sw logs to your local syslog.
\item Consider using a switch to increase log level (see\tosec{verbose}).
\end{itemize}

\subsection*{Do I have to configure my machines individually?}
\begin{itemize}
\item No, see \tosec{active}.
\end{itemize}

\subsection*{Can I configure my machines individually though?}
\begin{itemize}
\item Yes, see \tosec{passive}.
\end{itemize}

\subsection*{Why is the time wrong?}
\begin{itemize}
\item Times are stored as UTC, so notice your time zone.
\end{itemize}

\subsection*{Job files (import) cannot be read}
\begin{itemize}
\item Files have to be strictly in JSON, see \tosec{jobfileimport}
\item Please check privileges.
\end{itemize}

\subsection*{Data file (export) cannot be read}
\begin{itemize}
\item Please check privileges.
\item Can be removed if corrupted (though the auto run cycle will be reset).
\end{itemize}

\subsection*{Link opens task instead of report?}
\begin{itemize}
\item If there is no report (yet), yes, see\tosec{link}.
\end{itemize}

\subsection*{How can I see if at least one test was performed?}
\begin{itemize}
\item If \emph{severity} not equal to '-1', yes.
\end{itemize}

\subsection*{How can I see if OpenVAS tried to test, but failed?}
\begin{itemize}
\item If \emph{last\_attempt} > \emph{last\_report}.
\end{itemize}

\subsection*{Resolving IP addresses leads to strange results?}
\begin{itemize}
\item Indeed, it is not supported. Please see \tosec{plainipsonly}
\end{itemize}

\subsection*{Failed to acquire socket?}
\begin{itemize}
\item check if OpenVAS is running
\item check if OMP port is set correctly
\item check if firewall/fail2ban blocks OMP port
\end{itemize}

\subsection*{clean\_up\_threshold\_days does not always work?}
\begin{itemize}
\item You might have defined a job in your \emph{import machine list}, \tosec{jobimport}.
\end{itemize}

\subsection*{Can I exclude particular machines from scan?}
\begin{itemize}
\item You can add a job for this machine and set \emph{skip}, see\tosec{jobimport}.
\end{itemize}
